% !TeX spellcheck = en_US

% Author : Adam Sorrenti
%-------------------------
% FORKED FROM -- Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.08003pt}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{2.5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2\vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sorrenti.dev/}{\Large Adam Sorrenti}} & Email : \href{mailto:adamsorrenti8@hotmail.com}{adamsorrenti8@hotmail.com}\\
  \href{http://sorrenti.dev/}{http://sorrenti.dev/} & Mobile : \href{tel:+16475258773}{+1-647-525-8773} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ryerson University}{Toronto, ON}
      {Bachelor of Science (Hons.) in Computer Science;  GPA: 3.97/4.33}{Sept. 2018 -- Present}
      \resumeItemListStart
	      \resumeItem{Department of Computer Science Award}
	      {Top marks in Computer Science I \& II (CPS109 \& CPS209).}
	      \resumeItem{Google Developer Club Tech Lead}
	      {Ran programming workshops teaching C/C++, Python, and Data Structures with global out-reach.} %GDC is a network of university based groups for students interested in Google developer technologies.
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IBM}{Markham, ON}
      {Back-end Developer Intern}{May 2021 - Present}
      \resumeItemListStart
		\resumeItem{Testing}
	      {Participated in Agile Development environment, weekly scrum meetings, and other initiatives.}
        \resumeItem{Agile Development}
          {An environment valuing individuals and interactions, working software, customer collaboration, responding to change.}
        \resumeItem{Analytics}
          {Contributed to a multi-dimensional online analytical processing system using IBM Planning Analytics powered by TM1 in Prolog.}
      	\resumeItem{Continuous Integration}
     	  {Expanded automation within the teams Continuous Integration pipeline using Jenkins.}
      \resumeItemListEnd
      \resumeSubSubheading
		{CASCON x EVOKE Conference Volunteer}{Nov 2021}
		\resumeItemListStart
		\resumeItem{Speaker Support}
		{Supported academic/industry speakers prior to presentations with A/V assistance as well as helped speakers navigate the virtual conference environment.}
		\resumeItem{Academic Talks}
		{Participated, as a viewer, in Cognitive/AI Systems talks engaging with Q\&A about machine learning implementations.}
		
		\resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
	\resumeSubheading
	{Smart Nora}{Toronto, ON}
	{Software Consultant}{Oct 2021 - Dec 2021}
	\resumeItemListStart
	\resumeItem{Project Delivery}
	{Met with stakeholders to formalize software requirements specification and workflow. Provided technical documentation of code, algorithms, interfaces, and APIs.}
	\resumeItem{DataOps}
	{Setup, schema design and management of customer return labels generation using a third-party logistics REST API. Python was used on the application-level with continuous integration using cron jobs.}
	\resumeItemListEnd
	
    \resumeSubheading
      {Ryerson University}{Toronto, ON}
      {Mobile App Developer}{May 2020 - Apr 2021}
      \resumeItemListStart
        \resumeItem{Outreach}
        {Participated on a development team of senior and graduate students to deliver and maintain a mobile app which served more than 2,000 students campus-wide.}
        \resumeItem{Notifications}
        {Service for sending email, push and in-app notifications. Involved in features such as delivery time optimization, tracking, and grouping. Built an admin dashboard to run batch campaigns for marketing.}
        \resumeItem{Design}
        {Designed and implemented UI/UX features which correlated strongly to higher average user retention and engagement.}
      \resumeItemListEnd
%      \resumeSubSubheading
%      {Test Centre Assistant}{Sept 2019 - Apr 2020}
%      \resumeItemListStart
%      \resumeItem{Automation}
%      {}
%      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
  
\section{Projects}
	\resumeSubHeadingListStart
	\resumeSubItem{Sentimental Analysis of Amazon Reviews}
	{Comparative study of machine learning classification approaches.}
	\resumeSubItem{Multi-scale Face Detection}
	{Face Detection using SVM and Histogram of Oriented Gradients features.}
	\resumeSubItem{Optical Flow Estimation}
	{Implementation of Lucas-Kanade optical flow algorithm that computes the pixelwise motion between two images in a sequence.}
	\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, Javascript, C/C++, SQL, Java}
      \hfill
      \textbf{Technologies}{: Git, AWS, React, Unix, Docker}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
